Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-01-31 src/tex/ms.tex
expand hypothesis testing part

\subsubsection{Hypothesis testing}
To evaluate the evidence for correctly rejecting the null hypothesis, we employed the Mann-Whitney U test~\citep{Mann1947}.
%This is a non-parametric test to determine whether two independent samples were drawn from a population with the same distribution and is in particular sensitive to one sample being stochastically greater than the other.
This is a non-parametric test of the null hypothesis that two independent samples were drawn from a population with the same distribution and is in particular sensitive to one sample being stochastically greater than the other.
We used the Mann-Whitney U test to compare the distributions of \gls{NUV} fluxes of planets with and without biosignatures.
The implementation in Bioverse relies on the \texttt{scipy.stats.mannwhitneyu} function~\citep{Virtanen2020} and returns a p-value, for which we set a significance level of $\alpha = 0.05$ to reject the null hypothesis.
For every hypothesis test, we repeated randomized survey realizations to estimate the fraction of successful rejections of the null hypothesis, i.e., the statistical power of the survey.

>>>>

\subsubsection{Hypothesis testing}
%To evaluate the evidence for correctly rejecting the null hypothesis, we employed the Mann-Whitney U test~\citep{Mann1947}.
\rev{We ought to choose a statistical test that is sensitive to the UV~Threshold Hypothesis, and that could be realistically conducted in a future transit survey (which may include auxiliary information from ground-based observations, archived data, or models).
Given the available types of data expected from such surveys, our test shall be non-parametric and compare two samples -- planets with and without biosignatures -- to assess whether they are drawn from the same underlying population in terms of their infered historic maximum NUV flux.
Common options include the Kolmogorov-Smirnov test, the Brunner-Munzel test~\citep{Brunner2000}, and the Mann-Whitney U test~\citep{Mann1947}.
Due to its availability and suitability for large sample sizes, we chose the Mann-Whitney U test, which evaluates if one sample is stochastically greater than the other.
Here, we }
compare the distributions of \gls{NUV} fluxes of planets with and without biosignatures.
The implementation in Bioverse relies on the \texttt{scipy.stats.mannwhitneyu} function~\citep{Virtanen2020} and returns a p-value \rev{for each test.
To balance the trade-off between Type I and Type II error risks, we set the significance level to the widely adopted threshold $\alpha = 0.05$.
%This choice ensures a reasonable trade-off between detecting a potential dependence of biosignatures on NUV flux while controlling for statistical noise.
To quantify the diagnostic power of the survey, we conducted repeated randomized realizations and calculated the fraction of successful rejections of the null hypothesis, i.e., the statistical power.
}
